\documentclass[10pt, a4paper]{article}

% PACKAGES ===================================================
\usepackage[a4paper, margin=0.75in]{geometry} % Page margins
\usepackage{amsmath}                          % Math symbols
\usepackage{amsfonts}                         % Math fonts
\usepackage{amssymb}                          % Math symbols
\usepackage{graphicx}                         % Include graphics
\usepackage[utf8]{inputenc}                   % Input encoding
\usepackage[T1]{fontenc}                      % Font encoding
\usepackage{lmodern}                          % Use Latin Modern font (good default)
\usepackage{hyperref}                         % Clickable links
\usepackage{xcolor}                           % Color support
\usepackage{titlesec}                         % Section formatting
\usepackage{enumitem}                         % Custom lists
\usepackage{fontawesome5}                     % Icons (optional, requires fontawesome5 package)

% COLOR DEFINITIONS (Optional - customize as needed) =================
\definecolor{primary}{HTML}{2b2b2b}  % Dark grey for text
\definecolor{secondary}{HTML}{0e76a8} % Professional LinkedIn blue for better visibility
\definecolor{sectionrule}{HTML}{DDDDDD} % Light grey for rules

% HYPERLINK SETUP =============================================
\hypersetup{
    colorlinks=true,
    linkcolor=secondary,
    urlcolor=secondary,
    pdftitle={MD. Mehedi Hasan Maruf - Resume},
    pdfauthor={MD. Mehedi Hasan Maruf},
    pdfsubject={Software Engineer Resume},
    pdfkeywords={Software Engineer, Full-Stack, Python, Node.js, React, AI}
}

% FONT SETUP (Latin Modern is default, alternatives below) ======
% \usepackage{lato} % Example: Use Lato font
% \renewcommand*\familydefault{\sfdefault} % Make sans-serif the default if using Lato/similar

% PAGE STYLE ==================================================
\pagestyle{empty} % No page numbers
\setlength{\parindent}{0pt} % No paragraph indentation
\setlength{\parskip}{0.5em} % Space between paragraphs

% SECTION FORMATTING ==========================================
\titleformat{\section}
  {\Large\bfseries\color{secondary}} % Format: Large, bold, accent color
  {} % Label
  {0em} % Separation between label and title
  {} % Code before title
  [\titlerule] % Code after title (horizontal rule)
\titlespacing*{\section}{0pt}{1.5ex plus 1ex minus .2ex}{1.0ex plus .2ex}

\titleformat{\subsection}
  {\large\bfseries\color{primary}} % Format: large, bold, primary color
  {} % Label
  {0em} % Separation
  {} % Code before
\titlespacing*{\subsection}{0pt}{1ex plus .5ex minus .2ex}{0.5ex plus .2ex}

% CUSTOM COMMANDS (Optional) =================================
\newcommand{\datedsubsection}[2]{%
  \subsection*{#1 \hfill \small\textit{#2}}% Hides subsection number, adds date to the right
}

\newcommand{\resitem}[1]{\item #1} % Simple list item

% Make lists tighter
\setlist[itemize]{leftmargin=*, nosep, topsep=0.3ex, itemsep=0.3ex}
\setlist[description]{leftmargin=*, nosep, topsep=0.3ex, itemsep=0.3ex}

% HEADER ======================================================
\newcommand{\header}[8]{ % Added one argument for website URL placeholder
  \begin{center}
    {\Huge\bfseries\color{primary} #1}\\[0.2em] % Name
    {\Large\color{secondary} #2}\\[1em] % Title
    \small % Contact info
    \faPhone* \href{tel:#3}{#3} \quad | \quad
    \faEnvelope \href{mailto:#4}{\hspace{0.5mm}#4} \quad | \quad
    \faMapMarker {\hspace{1mm}#5 (#6)} \\ % Line break for better spacing if needed
    \faLinkedin \href{#7}{\hspace{0.5mm}mehedi-hasanmaruf} \quad | \quad
    \faGithub \href{#8}{\hspace{0.5mm}mehedi37}
    % --- Uncomment and add your website below ---
    % \quad | \quad \faGlobe \href{https://your-website.com}{your-website.com}
  \end{center}
  \vspace{1em}
}

% DOCUMENT START =============================================
\begin{document}
\color{primary} % Default text color

% --- Header ---
\header{MD. Mehedi Hasan Maruf} % Name
       {Software Engineer} % Title
       {+8801747090362} % Phone
       {mjmehedihasanoo7@gmail.com} % Email
       {Rajshahi} % City
       {Bangladesh} % Country
       {https://www.linkedin.com/in/mehedi-hasanmaruf} % LinkedIn URL
       {https://github.com/mehedi37} % GitHub URL

% --- Summary ---
\section*{Summary}
Extremely motivated Python software developer with specialisation in full-stack web development using Django and FastAPI and Node.js (React, Next.js). Looking to make cutting edge, scalable applications and tackle challenging
problems. Combines sound programming techniques and algorithmic design methodologies with practical experience in CI/CD, databases, and AI integration. Excited to leverage tech skills to tackle complicated projects and drive real-world impact in a growth role

% --- Skills ---
\section{Skills}
\begin{description}[style=unboxed, leftmargin=0pt, itemsep=0.2ex]
    \item[Programming Languages:] Python, JavaScript, TypeScript, C++, Java, PHP, Kotlin, Bash
    \item[Web Technologies:] Node.js, React.js, Next.js, Python FastAPI, Django, Angular, PHP Laravel
    \item[Databases:] MySQL, PostgreSQL, Supabase, Prisma
    \item[Tools \& Concepts:] Git, Docker, CI/CD (GitHub Actions, Bitbucket, Netlify), VPS (Linux) Management, REST APIs, ORM (Django ORM, Prisma), Project Management, Problem Solving
    \item[AI/ML:] LangGraph, Semantic Analysis, Natural Language Processing, Speech Recognition, Experience with ChatGPT \& LLAMA 2 integration
    \item[Other:] Redis
\end{description}

% --- Experience ---
\section{Experience}

\datedsubsection{Full Stack Developer}{Jan 2025 -- Present}
\textit{Aamira Software Solutions}, Kokomo, Indiana, USA
\begin{itemize}
    \resitem{Led development of a customer relationship management system that increased client response rates.}
    \resitem{Architected and implemented a microservice backend solution using Node.js that reduced API response time.}
    \resitem{Optimized database queries using Prisma, resulting in a 35\% improvement in application performance.}
\end{itemize}

\datedsubsection{AI Code Reviewer}{Oct 2024 -- Jan 2025}
\textit{Outlier}
\begin{itemize}
    \resitem{Reviewed and improved code quality for AI systems serving 50,000+ daily users.}
    \resitem{Implemented automated testing procedures that reduced bug rates by 22\% across the platform.}
    \resitem{Collaborated with senior developers to establish best practices for AI model integration.}
\end{itemize}

\datedsubsection{Industrial Trainee}{Feb 2025 -- Mar 2025}
\textit{Brain Station 23}, Dhaka, Bangladesh
\begin{itemize}
    \resitem{Gained practical experience in enterprise software development methodology and practices.}
    \resitem{Served as Team Representative for a 15-person cohort, coordinating communication between management and trainees.}
    \resitem{Contributed to a student AI system using Next and Node.js that was deployed to online server.}
\end{itemize}

\datedsubsection{Junior Software Engineer}{Nov 2022 -- Apr 2024}
\textit{Code Studio}, Rajshahi, Bangladesh
\begin{itemize}
    \resitem{Developed and maintained web backends supporting 15,000+ daily users using JavaScript, TypeScript, and Python (Django).}
    \resitem{Managed and maintained 12 Virtual Private Servers (Linux), achieving 99.8\% uptime over a two-year period.}
    \resitem{Established and optimized CI/CD pipelines that reduced deployment time by 40\% (GitHub Actions, Bitbucket, Netlify).}
    \resitem{Implemented Docker containerization that simplified deployment across 5 different client environments.}
\end{itemize}

\datedsubsection{Competitive Programming Teacher}{Aug 2023 -- Nov 2023}
\textit{RAPL (University Organization)}
\begin{itemize}
    \resitem{Instructed RUET students in competitive programming concepts and algorithms, with 80\% showing improved contest performance.}
    \resitem{Developed curriculum covering number theory (GCD, Fermat's Little Theorem) and graph traversal (BFS, DFS).}
    \resitem{Organized biweekly coding competitions to reinforce practical application of theoretical concepts.}
\end{itemize}

% --- Projects ---
\section{Personal Projects}

\datedsubsection{BareMinimum Chatbot - Full Stack AI Application}{Feb 2025 -- Mar 2025}
\textit{Repository:} \href{https://github.com/mehedi37/BareMinimumChatBot}{BareMinimumChatBot} \textit{(Backend)}, \href{https://github.com/mehedi37/bare-minimum-bot}{bare-minimum-bot} \textit{(Frontend)}
\begin{itemize}
    \resitem{Developed during industrial attachment at Brain Station 23 as a comprehensive AI-powered chatbot system.}
    \resitem{Engineered a FastAPI backend with structured endpoints for chat interactions, content summarization, and quiz generation.}
    \resitem{Created RESTful API integration with local LLM models (Ollama) for privacy-focused AI interactions.}
    \resitem{Built a responsive Next.js frontend with modern UI components implementing cookie-based session tracking and history preservation.}
    \resitem{Implemented advanced content processing features including YouTube video summarization, PDF document analysis, and custom quiz generation.}
\end{itemize}

\datedsubsection{ProjectPika - Virtual Voice Assistant}{Sep 2020 -- Mar 2022}
\textit{Repository:} \href{https://github.com/mehedi37/projectPika}{github.com/mehedi37/projectPika}
\begin{itemize}
    \resitem{Developed a custom voice assistant using Python, incorporating NLP, speech recognition, and AI.}
    \resitem{Implemented multi-language recognition with English translation capabilities.}
    \resitem{Engineered a flexible command system for tasks like weather checks and scheduling.}
    \resitem{Integrated both ChatGPT and local LLAMA 2 models for enhanced AI interaction.}
    \resitem{Enabled direct schedule retrieval from online Google Sheets via voice commands.}
\end{itemize}

\datedsubsection{Hotel Management System}{Jan 2024 -- Mar 2024}
\textit{Repository:} \href{https://github.com/mehedi37/hotel_management}{github.com/mehedi37/hotel\_management}
\begin{itemize}
    \resitem{Developed during EDGE programming course on PHP Laravel as my final project.}
    \resitem{Developed a PHP-based hotel room management system with secure authentication and CRUD operations.}
    \resitem{Implemented comprehensive security features including password hashing, CSRF protection, and SQL injection prevention using PDO.}
    \resitem{Built a responsive web interface using Bootstrap UI for seamless operation across different devices.}
    \resitem{Designed a robust database schema for efficient room management, bookings, and administrative operations.}
    \resitem{Deployed the application with continuous 99.8\% uptime on a live server with multi-user support.}
\end{itemize}

\datedsubsection{Gamers Heaven - E-commerce Platform}{Dec 2023 -- Feb 2024}
\textit{Repository:} \href{https://github.com/mehedi37/gamers_heaven}{github.com/mehedi37/gamers\_heaven}
\begin{itemize}
    \resitem{Designed and implemented a full-featured e-commerce platform for gaming products using ASP.NET Core MVC with C\#.}
    \resitem{Architected a secure user management system with role-based access control using ASP.NET Identity.}
    \resitem{Developed a comprehensive shopping cart system with product management, user authentication, and order processing.}
    \resitem{Implemented Entity Framework Core with code-first approach for database management and migrations.}
    \resitem{Built a responsive front-end using Bootstrap with Razor views for dynamic content rendering.}
\end{itemize}

\datedsubsection{Thesis Site}{Apr 2024 -- Apr 2024}
\textit{Repository:} \href{https://github.com/mehedi37/Thesis_Site}{github.com/mehedi37/Thesis\_Site}
\begin{itemize}
    \resitem{Developed a full-featured academic thesis management platform using Django.}
    \resitem{Implemented role-based access control system supporting 200+ concurrent users (students, faculty, and administrators).}
    \resitem{Engineered automated document verification process using Django's ORM that eliminated manual verification steps.}
    \resitem{Integrated with university authentication systems using OAuth for seamless single sign-on experience.}
\end{itemize}

% --- Education ---
\section{Education}

\datedsubsection{B.Sc. Engineering, Computer Science and Engineering}{Mar 2022 -- Present}
\textit{Rajshahi University of Engineering \& Technology (RUET)}, Rajshahi, Bangladesh
\begin{itemize}
    \resitem{Current Semester: 6th semester}
    \resitem{CGPA: 3.73 (till 5th semester)}
\end{itemize}

% \datedsubsection{Higher Secondary Certificate (H.S.C), Science}{Mar 2018 -- Feb 2020}
% \textit{Police Lines School \& College}, Rangpur, Bangladesh

% \datedsubsection{Secondary School Certificate (S.S.C), Science}{Jan 2016 -- Jan 2018}
% \textit{Police Lines School \& College}, Rangpur, Bangladesh


% --- Certifications ---
\section{Certifications \& Achievements}
\begin{itemize}
    \resitem{PHP (Laravel) - EDGE Project: \href{https://training.edge.gov.bd/certificate-validation?certificate_no=EDGE-DSTS-116-6631-00012}{View Certificate} (Feb 2025)}
    \resitem{Python (Basic) - HackerRank: \href{https://www.hackerrank.com/certificates/0550b52e4c2b}{View Certificate} (Jun 2023)}
    \resitem{4th Place - RUET CodeSmash (Team Competition) - Competitive Programming Contest (March 2023)}
    \resitem{4th Place - RUET CodeSpark (Individual) - Competitive Programming Contest (Oct 2022)}
\end{itemize}

% --- Languages ---
\section{Languages}
\begin{itemize}
    \resitem{Bangla (Native)}
    \resitem{English (Full Professional Proficiency)}
\end{itemize}

% --- Interests ---
\section{Interests}
Artificial Intelligence, Machine Learning, Full-Stack Development (Node.js, Python), Competitive Programming, Cloud Technologies, Open Source Contribution

% DOCUMENT END ===============================================
\end{document}