\documentclass[10pt, a4paper]{article}

% PACKAGES ===================================================
\usepackage[a4paper, margin=0.75in]{geometry} % Page margins
\usepackage{amsmath}                          % Math symbols
\usepackage{amsfonts}                         % Math fonts
\usepackage{amssymb}                          % Math symbols
\usepackage{graphicx}                         % Include graphics
\usepackage[utf8]{inputenc}                   % Input encoding
\usepackage[T1]{fontenc}                      % Font encoding
\usepackage{lmodern}                          % Use Latin Modern font (good default)
\usepackage{hyperref}                         % Clickable links
\usepackage{xcolor}                           % Color support
\usepackage{titlesec}                         % Section formatting
\usepackage{enumitem}                         % Custom lists
\usepackage{fontawesome5}                     % Icons (optional, requires fontawesome5 package)

% COLOR DEFINITIONS (Optional - customize as needed) =================
\definecolor{primary}{HTML}{2b2b2b}  % Dark grey for text
\definecolor{secondary}{HTML}{0e76a8} % Professional LinkedIn blue for better visibility
\definecolor{sectionrule}{HTML}{DDDDDD} % Light grey for rules

% HYPERLINK SETUP =============================================
\hypersetup{
    colorlinks=true,
    linkcolor=secondary,
    urlcolor=secondary,
    pdftitle={MD. Mehedi Hasan Maruf - Resume},
    pdfauthor={MD. Mehedi Hasan Maruf},
    pdfsubject={Software Engineer Resume},
    pdfkeywords={Software Engineer, Full-Stack, Python, Node.js, React, AI}
}

% FONT SETUP (Latin Modern is default, alternatives below) ======
% \usepackage{lato} % Example: Use Lato font
% \renewcommand*\familydefault{\sfdefault} % Make sans-serif the default if using Lato/similar

% PAGE STYLE ==================================================
\pagestyle{empty} % No page numbers
\setlength{\parindent}{0pt} % No paragraph indentation
\setlength{\parskip}{0.3em} % Reduced space between paragraphs

% SECTION FORMATTING ==========================================
\titleformat{\section}
  {\Large\bfseries\color{secondary}} % Format: Large, bold, accent color
  {} % Label
  {0em} % Separation between label and title
  {} % Code before title
  [\titlerule] % Code after title (horizontal rule)
\titlespacing*{\section}{0pt}{1.2ex plus 1ex minus .2ex}{0.8ex plus .2ex}

\titleformat{\subsection}
  {\large\bfseries\color{primary}} % Format: large, bold, primary color
  {} % Label
  {0em} % Separation
  {} % Code before
\titlespacing*{\subsection}{0pt}{0.8ex plus .5ex minus .2ex}{0.3ex plus .2ex}

% COMPANY URLs (Update links here) ===========================
\newcommand{\urlAamira}{https://aamira.ca/}
\newcommand{\urlOutlier}{https://www.linkedin.com/company/try-outlier/}
\newcommand{\urlBrainStation}{https://brainstation-23.com/}
\newcommand{\urlCodeStudio}{https://www.linkedin.com/company/code-studio4/}

% CUSTOM COMMANDS (Optional) =================================
\newcommand{\datedsubsection}[2]{%
  \subsection*{#1 \hfill \small\textit{#2}}% Hides subsection number, adds date to the right
}

\newcommand{\resitem}[1]{\item #1} % Simple list item

% Make lists tighter
\setlist[itemize]{leftmargin=*, nosep, topsep=0.3ex, itemsep=0.3ex}
\setlist[description]{leftmargin=*, nosep, topsep=0.3ex, itemsep=0.3ex}

% HEADER ======================================================
\newcommand{\header}[9]{ % Added argument for WhatsApp
  \begin{center}
    {\Huge\bfseries\color{primary} #1}\\[0.2em] % Name
    {\Large\color{secondary} #2}\\[1em] % Title
    \small % Contact info
    \faPhone* \href{tel:#3}{#3} \quad | \quad
    \faWhatsapp \href{https://wa.me/#4}{#4} \quad | \quad
    \faEnvelope \href{mailto:#5}{\hspace{0.5mm}#5} \quad | \quad
    \faMapMarker {\hspace{1mm}#6 (#7)} \\ % Line break for better spacing if needed
    \faLinkedin \href{#8}{\hspace{0.5mm}mehedi-hasanmaruf} \quad | \quad
    \faGithub \href{#9}{\hspace{0.5mm}mehedi37}
    % --- Uncomment and add your website below ---
    \quad | \quad \faGlobe \href{https://www.mehedi-hasan-maruf.me/}{\hspace{0.5mm}mehedi-hasan-maruf.me}
  \end{center}
  \vspace{0.5em}
}

% DOCUMENT START =============================================
\begin{document}
\color{primary} % Default text color

% --- Header ---
\header{MD. Mehedi Hasan Maruf} % Name
       {Software Engineer} % Title
       {+8801747090362} % Phone
       {+8801533300089} % WhatsApp
       {mjmehedihasanoo7@gmail.com} % Email
       {Rajshahi} % City
       {Bangladesh} % Country
       {https://www.linkedin.com/in/mehedi-hasanmaruf} % LinkedIn URL
       {https://github.com/mehedi37} % GitHub URL

% --- Summary ---
% \section*{Summary}
% Extremely motivated software engineer with specialization in full-stack web development using Django and FastAPI and Node.js (React, Next.js). Looking to make cutting-edge, scalable applications and tackle challenging
% problems. Combines sound programming techniques and algorithmic design methodologies with practical experience in CI/CD, databases, and AI integration. Excited to leverage tech skills to tackle complicated projects and drive real-world impact in a growth role

% --- Skills ---
\section{Skills}
\begin{description}[style=unboxed, leftmargin=0pt, itemsep=0.2ex]
    \item[Programming Languages:] Python, JavaScript, TypeScript
    \item[Web Technologies:] Node.js, React.js, Angular, Next.js, FastAPI, Django
    \item[Databases:] MySQL, PostgreSQL, MongoDB, Supabase
    \item[Tools \& Concepts:] Git, Docker, CI/CD (GitHub Actions, Netlify), VPS (Linux) Management, REST APIs, ORM (Django ORM, Supabase), Project Management, Problem Solving
    \item[AI/ML:] LangChain, Semantic Analysis, NLP
\end{description}

% --- Experience ---
\section{Experience}

\datedsubsection{Full Stack Developer}{Jan 2025 -- Present}
\textit{Aamira Software Solutions} \href{\urlAamira}{\small\faExternalLink*}, Kokomo, Indiana, USA
\begin{itemize}
    \resitem{Led development of a customer relationship management system that increased client response rates.}
    \resitem{Architected and implemented a Typescript microservice backend solution that reduced API response time.}
    \resitem{Optimized database queries using Supabase, resulting in significant improvements in application performance.}
\end{itemize}

\datedsubsection{AI Code Reviewer}{Oct 2024 -- Jan 2026}
\textit{Outlier} \href{\urlOutlier}{\small\faExternalLink*}
\begin{itemize}
    \resitem{Reviewed and improved code quality for AI systems serving 50,000+ daily users.}
    \resitem{Collaborated with senior developers to establish best practices for AI model integration.}
\end{itemize}

\datedsubsection{Industrial Trainee}{Feb 2025 -- Mar 2025}
\textit{Brain Station 23} \href{\urlBrainStation}{\small\faExternalLink*}, Dhaka, Bangladesh
\begin{itemize}
    \resitem{Gained practical experience in enterprise software development methodology and practices.}
    \resitem{Served as Team Representative for a 15-person cohort, coordinating communication between management and trainees.}
    \resitem{Contributed to a student AI system using Next and Node.js that was deployed to an online server.}
\end{itemize}

\datedsubsection{Junior Software Engineer}{Nov 2022 -- Apr 2024}
\textit{Code Studio} \href{\urlCodeStudio}{\small\faExternalLink*}, Rajshahi, Bangladesh
\begin{itemize}
    \resitem{Developed backends supporting thousands of daily users using JavaScript, TypeScript, and Python (Django).}
    \resitem{Managed 12 VPS (Linux) with 99.8\% uptime and optimized CI/CD pipelines, reducing deployment time by 40\%.}
    \resitem{Implemented Docker containerization, simplifying deployment across 5 different client environments.}
\end{itemize}

\datedsubsection{Competitive Programming Mentor}{Aug 2023 -- Nov 2023}
\textit{RAPL (University Organization)}
\begin{itemize}
    \resitem{Instructed RUET students in competitive programming concepts.}
    \resitem{Developed curriculum covering number theory and graph traversal algorithms; organized biweekly coding competitions.}
\end{itemize}

% --- Projects ---
\section{Personal Projects}

\datedsubsection{StudentAI - Intelligent Learning Companion}{Feb 2025 -- Mar 2025}
\textit{Repository:} \href{https://github.com/mehedi37/student_AI}{student\_AI} \textit{(Backend)}, \href{https://github.com/mehedi37/student_ai_next}{student\_ai\_next} \textit{(Frontend)} | \textit{Live:} \href{https://student-ai-next.vercel.app/}{student-ai-next.vercel.app}
\begin{itemize}
    \resitem{Developed during industrial attachment at Brain Station 23: AI-powered learning assistant combining \textbf{FastAPI backend} with \textbf{Next.js frontend} for personalized education.}
    \resitem{Implemented intelligent quiz generation, document Q\&A, and YouTube content analysis using LangChain and semantic search with conversation memory.}
    \resitem{Built a comprehensive document processing pipeline supporting PDFs, images, and videos with real-time WebSocket chat, JWT authentication, and progress tracking.}
    \resitem{Deployed production-ready application on Vercel (frontend) and Render (backend) with Supabase database integration.}
\end{itemize}

\datedsubsection{Thesis Site (Django)}{March 2024 -- May 2024}
\textit{Repository:} \href{https://github.com/mehedi37/Thesis_Site}{github.com/mehedi37/Thesis\_Site}
\begin{itemize}
    \resitem{Developed \textbf{PYTHON-Django} thesis topic post. Supervisor and students can communicate better way.}
    \resitem{Built a responsive Bootstrap UI interface with comprehensive CRUD operations for efficient communication between student(s), supervisor, authority.}
\end{itemize}


% --- Education ---
\section{Education}

\datedsubsection{B.Sc. Engineering, Computer Science and Engineering}{Mar 2022 -- Present}
\textit{Rajshahi University of Engineering \& Technology (RUET)}, Rajshahi, Bangladesh
\begin{itemize}
    \resitem{Current Semester: 8th semester}
    \resitem{CGPA: 3.77 (till 7th semester)}
\end{itemize}

% \datedsubsection{Higher Secondary Certificate (H.S.C), Science}{Mar 2018 -- Feb 2020}
% \textit{Police Lines School \& College}, Rangpur, Bangladesh

% \datedsubsection{Secondary School Certificate (S.S.C), Science}{Jan 2016 -- Jan 2018}
% \textit{Police Lines School \& College}, Rangpur, Bangladesh


% --- Certifications ---
\section{Certifications \& Achievements}
\begin{itemize}
    \resitem{Digital Accessibility Training (DAT) - a2i (Aspire to Innovate), Govt. of Bangladesh \href{https://drive.google.com/file/d/1r0YTwNWt2G--afHjJkN7hf9taI2d445W/view?usp=sharing}{\faExternalLink*} (Oct 2025)}
    \resitem{Industrial Training Certificate - Brain Station 23 \href{https://drive.google.com/file/d/1_Smp7BMAuuKgN4McPJv-UFcsK27mXtBj/view?usp=sharing}{\faExternalLink*} (Mar 2025)}
    \resitem{PHP (Laravel) - EDGE Project \href{https://training.edge.gov.bd/certificate-validation?certificate_no=EDGE-DSTS-116-6631-00012}{\faExternalLink*} (Feb 2025)}
    \resitem{Experience Certificate - Code Studio \href{https://drive.google.com/file/d/195bms3HX2eF-QGjPypnlaZmQLn2nv7xT/view?usp=sharing}{\faExternalLink*} (Apr 2024)}
    \resitem{4th Place - RUET CodeSmash (Team Competition) - Competitive Programming Contest \href{https://drive.google.com/file/d/1ESOpq2KagzqafmpEjau5RvhTNeop4FKN/view?usp=sharing}{\faExternalLink*} (Mar 2023)}
    \resitem{4th Place - RUET CodeSpark (Individual) - Competitive Programming Contest \href{https://drive.google.com/file/d/18CvmRA4xr3TkCpSjNxsQMxBSmh_yQUQz/view?usp=sharing}{\faExternalLink*} (Oct 2022)}
\end{itemize}

% --- Languages ---
% \section{Languages}
% \begin{itemize}
%     \resitem{Bangla (Native)}
%     \resitem{English (Full Professional Proficiency)}
%     \resitem{Japanese (A1 level)}
% \end{itemize}

% --- Interests ---
% \section{Interests}
% 3D Design, Artificial Intelligence, Machine Learning, Full-Stack Development (Node.js, Python), Competitive Programming, Cloud Technologies, Open Source Contribution

% DOCUMENT END ===============================================
\end{document}